---
title: "Trust-level Covid-19 hospital admissions forecasts"
author: "Sophie Meakin, Sam Abbott, Seb Funk"
date: "`r format.Date(Sys.Date(), format = '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 14, fig.height = 9)

library(tidyverse)
library(ggrepel)
library(patchwork)
library(covidregionaldata)
library(covid19.nhs.data)

source(here::here("R", "load_data_fns.R"))
source(here::here("R", "plot_fns.R"))
source(here::here("R", "utils.R"))

forecast_date <- as.Date("2022-02-25")
areas <- c()

```

```{r new variables, include = FALSE}

flag_utlas <- readRDS(file = here::here("current_forecasts", "data", "flagged_utlas.rds"))
exclude_utlas <- flag_utlas$id_name

manual_remove <- tibble::tibble(trust_code = c(), trust_name = NA, n = NA, utla_names = NA, label = NA)

exclude_trusts <- covid19.nhs.data::trust_utla_mapping %>%
  covid19.nhs.data::get_names() %>%
  dplyr::filter(geo_name %in% exclude_utlas,
                p_geo > 0.2) %>%
  dplyr::group_by(trust_code, trust_name) %>%
  dplyr::summarise(n = n(),
                   utla_names = paste(geo_name, collapse = ", ")) %>%
  dplyr::mutate(label = ifelse(n == 1,
                               paste0(trust_name, " (UTLA: ", utla_names, ")" ),
                               paste0(trust_name, " (UTLAs: ", utla_names, ")" )))

# Custom palettes
col_ensemble <- RColorBrewer::brewer.pal(n=3,"Set2")[1]
col_epinow2 <- RColorBrewer::brewer.pal(n=3,"Set2")[2]
col_timeser <- technocolour::technocolours(name = "ibrik", n = 6)[5]
col_convoln <- technocolour::technocolours(name = "fluorescent_rush", n = 6)[2]

```

```{r observed, include = FALSE}

admissions <- load_hospital_data(keep_data = c("all_adm"), add_private = TRUE) %>%
  dplyr::rename(adm = all_adm) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))
  # dplyr::filter(!id %in% exclude_trusts$trust_code)

plot_trusts_observed <- admissions %>%
  dplyr::filter(date > forecast_date - 28,
                date <= forecast_date) %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(total_adm = sum(adm, na.rm = TRUE)) %>%
  dplyr::arrange(-total_adm) %>%
  dplyr::slice_head(n = 25) %>%
  dplyr::pull(id)

 trusts_observed7 <- admissions %>%
  dplyr::filter(date > forecast_date - 7,
                date <= forecast_date) %>%
  dplyr::group_by(nhs_region, id) %>%
  dplyr::summarise(observed = mean(adm, na.rm = TRUE))

```

# Summary

The current forecast date is **`r format.Date(forecast_date, format = "%d %B")`**, showing data until **`r format.Date(max(admissions$date, na.rm = TRUE), format = "%d %B")`**.

**`r ifelse(length(exclude_trusts$label)>0, "The following Trusts/UTLAs make forecasts of hospital admissions using timeseries forecasts of COVID-19 cases (rather than EpiNow2, by default):", "")`** `r paste0(exclude_trusts$label, collapse = ", ")`

The main forecasting model is an unweighted ensemble of three individual models:

1. unweighted time series ensemble model (autoregressive ARIMA, ETS and naive models)
2. regression + 7-day-lagged cases (cases mapped from UTLA to Trust using Trust-UTLA mapping in `covid19.nhs.data`)
3. convolution from cases to admissions (scaled; cases mapped to Trusts as above)

The time series ensemble and regression models are trained on the last 6 weeks of data from `r format.Date(forecast_date - 6*7, format = "%d %B")`; the case-convolution model is trained on the last 9 weeks of data (from `r format.Date(forecast_date - 9*7, format = "%d %B")`), of which 6 are used in the likelihood. Forecasts are made for the following 14 days.

For details of the fitted models, see our preprint ["Comparative assessment of methods for short-term forecasts of COVID-19 admissions in England at the local level"](https://www.medrxiv.org/content/10.1101/2021.10.18.21265046v1).


```{r load forecasts}

# Current forecast summary
current_forecast <- readRDS(file = here::here("current_forecasts",
                                              "data",
                                              "admissions_trust",
                                              paste0("admissions_", forecast_date, ".rds"))) %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90) %>%
  dplyr::filter(horizon <= 14) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))
  # dplyr::filter(!id %in% exclude_trusts$trust_code)

# Current regional forecast
region_forecast <- readRDS(file = here::here("current_forecasts",
                                              "data",
                                              "admissions_region",
                                              paste0("admissions_", forecast_date, ".rds"))) %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90) %>%
  dplyr::filter(horizon <= 14)

# Current forecast samples
current_forecast_long <- readRDS(file = here::here("current_forecasts",
                                                   "data",
                                              "admissions_trust",
                                              paste0("admissions_long_", forecast_date, ".rds")))

# All past forecasts
file_dir <- here::here("current_forecasts", "data", "admissions_trust")
file_names <- list.files(file_dir)[which(!grepl("latest", list.files(file_dir)) &
                                           !grepl("long", list.files(file_dir)) &
                                           !grepl(forecast_date, list.files(file_dir)))]
all_forecasts <- purrr::map_df(.x = file_names, .f = ~ {
  
  out <- readRDS(file = here::here(file_dir, .x))
  return(out)
  
}) %>%
  dplyr::bind_rows() %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))

## All regional forecasts
file_dir <- here::here("current_forecasts", "data", "admissions_region")
file_names <- list.files(file_dir)[which(!grepl(forecast_date, list.files(file_dir)))]
all_reg_forecasts <- purrr::map_df(.x = file_names, .f = ~ {
  
  if(grepl("epinow2", .x)){
    
    file_date <- .x %>%
      stringr::str_remove(".csv") %>%
      stringr::str_remove("epinow2_admisssions_") %>%
      as.Date()
    
    out <- readr::read_csv(file = here::here(file_dir, .x)) %>%
      dplyr::filter(type == "forecast") %>%
      dplyr::mutate(forecast_from = file_date,
                    horizon = as.integer(date - forecast_from)) %>%
      dplyr::select(-c(strat, type, mean, sd)) %>%
      dplyr::rename(lower_0 = median) %>%
      tidyr::pivot_longer(cols = c(lower_90, lower_50, lower_20, lower_0, upper_20, upper_50, upper_90), names_to = "quantile_label") %>%
      dplyr::mutate(model = "EpiNow2") %>%
      dplyr::select(forecast_from, id = region, horizon, date_horizon = date, quantile_label, value, model)
    
  } else {
    
    out <- readRDS(file = here::here(file_dir, .x)) %>%
      dplyr::select(-quantile)
    
  }
  return(out)
  
}) %>%
  dplyr::bind_rows() %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90)


# 7- and 14-day median forecast + current 7-day average
forecast_point <- current_forecast %>%
  dplyr::filter(model == "mean_ensemble",
                horizon %in% c(7, 14)) %>%
  dplyr::select(id, horizon, median) %>%
  dplyr::mutate(horizon = paste0("forecast_", horizon)) %>%
  tidyr::pivot_wider(id_cols = id, names_from = horizon, values_from = median) %>%
  dplyr::left_join(trusts_observed7, by = "id") %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::select(nhs_region, id, trust_name, observed, forecast_7, forecast_14)

# 7- and 14-day probability of increase
forecast_prob <- current_forecast_long %>%
  dplyr::filter(model == "mean_ensemble",
                horizon %in% c(7, 14)) %>%
  dplyr::left_join(trusts_observed7, by = c("id")) %>%
  dplyr::mutate(observed = round(observed)) %>%
  dplyr::group_by(forecast_from, id, horizon) %>%
  dplyr::filter(value > observed) %>%
  dplyr::group_by(forecast_from, id, horizon) %>%
  dplyr::filter(quantile == min(quantile)) %>%
  dplyr::mutate(horizon = paste0("p_", horizon),
                p_increase = 1-quantile) %>%
  dplyr::ungroup() %>%
  dplyr::select(id, horizon, p_increase) %>%
  unique() %>%
  tidyr::pivot_wider(id_cols = -c(horizon, p_increase), names_from = horizon, values_from = p_increase)
  # dplyr::filter(!id %in% exclude_trusts$trust_code)

# Current forecast summary table
current_forecast_tb <- forecast_point %>%
  dplyr::left_join(forecast_prob, by = "id") %>%
  dplyr::select(nhs_region, id, trust_name, observed, forecast_7, p_7, forecast_14, p_14) %>%
  dplyr::mutate(observed = round(observed, 1),
                p_7 = round(p_7, 2),
                p_14 = round(p_14, 2))

# Data for scatter plot
scatter_data <- current_forecast_tb %>%
  dplyr::ungroup() %>%
  dplyr::mutate(change = forecast_14 - observed,
                label = ifelse(observed >= 1 & (observed > quantile(observed, 0.9, na.rm = TRUE) |
                                 p_14 > quantile(p_14, 0.9, na.rm = TRUE) |
                                 p_14 == 0.99),
                               trust_name, NA),
                label = stringr::str_wrap(label, width = 25))

```

```{r include = FALSE}

return_region_plots <- function(region = "North West"){
  
  tb_summary <- DT::datatable(data = current_forecast_tb %>%
                                dplyr::filter(nhs_region == region) %>%
                dplyr::select(`NHS region` = nhs_region,
                              ID = id,
                              Name = trust_name,
                              `Current 7-day average` = observed,
                              `One-week ahead forecast` = forecast_7,
                              `Two-weeks ahead forecast` = forecast_14,
                              `14-day probability of increase` = p_14),
              rownames = FALSE,
              )
  
  g_current <- plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 28,
                                      date <= forecast_date) %>%
                        dplyr::rename(observed = adm),
                      forecast = current_forecast,
                     trusts = unique(current_forecast_tb$id[which(current_forecast_tb$nhs_region == region & current_forecast_tb$observed >= 0.7)]),
                     models = "mean_ensemble",
                     facet_models = FALSE) +
  scale_x_date(breaks = "1 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  labs(title = region,
       subtitle = "Ensemble model",
       caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data
  geom_line(data = admissions %>%
                        dplyr::filter(nhs_region == region,
                                      id %in% unique(current_forecast_tb$id[which(current_forecast_tb$nhs_region == region & current_forecast_tb$observed >= 0.7)]),
                                      date >= forecast_date) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed), lty = 2)
  
  g_current_conv <- plot_forecast_ribbons(observed = admissions %>%
                          dplyr::filter(date > forecast_date - 28,
                                        date <= forecast_date) %>%
                          dplyr::rename(observed = adm),
                        forecast = current_forecast,
                       trusts = unique(current_forecast_tb$id[which(current_forecast_tb$nhs_region == region & current_forecast_tb$observed >= 0.7)]),
                       models = "convolution_rt",
                       facet_models = FALSE) +
    scale_x_date(breaks = "1 weeks", date_labels = "%d %b") +
    scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
    scale_color_brewer(palette = "Set1") +
    scale_fill_brewer(palette = "Set1") +
    labs(title = region,
         subtitle = "Case-convolution model",
         caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
    theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
    ## Adding current observed data
    geom_line(data = admissions %>%
                          dplyr::filter(nhs_region == region,
                                        id %in% unique(current_forecast_tb$id[which(current_forecast_tb$nhs_region == region & current_forecast_tb$observed >= 0.7)]),
                                        date >= forecast_date) %>%
                          dplyr::rename(observed = adm),
              aes(x = date, y = observed), lty = 2)
  
  g_scatter <- scatter_data %>%
    ggplot(aes(x = p_14, y = observed)) +
    geom_point(size = 3, col = "grey90") +
    geom_text_repel(data = scatter_data %>%
                      dplyr::filter(nhs_region == region),
                    aes(label = label),
                    size = 3, col = "grey20",
                    point.padding = 0.2, min.segment.length = 0.1) +
    scale_x_continuous(limits = c(0, 1)) +
    scale_y_continuous(limits = c(0, NA), breaks = seq(0, 100, 10)) +
    scale_color_fermenter(n.breaks = 7, palette = "RdBu", limits = max(abs(scatter_data$change))*c(-1, 1)) +
    labs(x = "Probability of increase (14 days ahead)", y = "Current admissions (7-day average)",
         title = region,
         subtitle = "Ensemble model",
         caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
         col = "Forecast\nchange") +
    theme_bw()
  g_scatter <- g_scatter +
    geom_point(data = scatter_data %>%
                 dplyr::filter(nhs_region == region),
               aes(col = change), size = 3)
  
  g_past7 <- plot_forecast_bars(observed = admissions %>%
                         dplyr::filter(date >= forecast_date - 84) %>%
                         dplyr::rename(observed = adm),
                     forecast = all_forecasts,
                     h = 7,
                     trusts = unique(admissions$id[which(admissions$nhs_region == region)]),
                     models = "mean_ensemble",
                     facet_models = FALSE) +
    scale_x_date(limits = c(forecast_date - 63, forecast_date + 1),
                 breaks = "2 weeks", date_labels = "%d %b") +
    scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
    labs(title = region,
         subtitle = "7-day ahead forecasts, ensemble model") +
    theme(legend.position = "none")

  g_past14 <- plot_forecast_bars(observed = admissions %>%
                         dplyr::filter(date >= forecast_date - 84) %>%
                         dplyr::rename(observed = adm),
                     forecast = all_forecasts,
                     h = 14,
                     trusts = unique(admissions$id[which(admissions$nhs_region == region)]),
                     models = "mean_ensemble",
                     facet_models = FALSE) +
    scale_x_date(limits = c(forecast_date - 63, forecast_date + 1),
                 breaks = "2 weeks", date_labels = "%d %b") +
    scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
    labs(title = region,
         subtitle = "14-day ahead forecasts, ensemble model") +
    theme(legend.position = "none")
  
  return(list(table_summary = tb_summary,
              current_forecast = g_current,
              current_forecast_convolution = g_current_conv,
              scatter = g_scatter,
              past_7days = g_past7,
              past_14days = g_past14))
  
}

```

# Current forecasts {.tabset}

## Trusts, all regions {.tabset .tabset-pills}

### Summary, table

```{r overall}

# Table
DT::datatable(data = current_forecast_tb %>%
                dplyr::select(`NHS region` = nhs_region,
                              ID = id,
                              Name = trust_name,
                              `Current 7-day average` = observed,
                              `One-week ahead forecast` = forecast_7,
                              `Two-weeks ahead forecast` = forecast_14,
                              `14-day probability of increase` = p_14),
              rownames = FALSE,
              )

```

### Current forecast, ribbon {.active}

```{r}

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 28,
                                      date <= forecast_date) %>%
                        dplyr::rename(observed = adm),
                      forecast = current_forecast,
                     trusts = plot_trusts_observed,
                     models = "mean_ensemble",
                     facet_models = FALSE) +
  scale_x_date(breaks = "1 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  labs(title = "Top 25 Trusts with most admissions in last 28 days",
       subtitle = "Ensemble model",
       caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data (dashed)
  geom_line(data = admissions %>%
                        dplyr::filter(id %in% plot_trusts_observed,
                                      date >= forecast_date) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed), lty = 2)
  ## Adding trend line (red)
  # geom_line(data = admissions %>%
  #                       dplyr::filter(date > forecast_date - 28,
  #                                     id %in% plot_trusts_observed) %>%
  #                       dplyr::group_by(id) %>%
  #                       tidyr::fill(adm) %>%
  #                       dplyr::mutate(adm_trend = (stl(ts(adm, freq = 7), s.window = 7)$time.series)[,2]),
  #           aes(x = date, y = adm_trend), col = "tomato")

```

### Forecast increase, scatter

```{r}

scatter_data %>%
  ggplot(aes(x = p_14, y = observed, col = change)) +
  geom_point(size = 3) +
  geom_text_repel(aes(label = label), size = 3, col = "grey20",
                  point.padding = 0.2, min.segment.length = 0.1) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 100, 10)) +
  scale_color_fermenter(n.breaks = 7, palette = "RdBu", limits = max(abs(scatter_data$change))*c(-1, 1)) +
  labs(x = "Probability of increase (14 days ahead)", y = "Current admissions (7-day average)",
       title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       subtitle = "Ensemble model",
       col = "Forecast\nchange") +
  theme_bw()

# Facetted by NHS region
scatter_data %>%
  ggplot(aes(x = p_14, y = observed, col = change)) +
  geom_point(size = 3) +
  geom_text_repel(aes(label = label), size = 3, col = "grey20",
                  point.padding = 0.2, min.segment.length = 0.1) +
  facet_wrap(. ~ nhs_region) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 100, 10)) +
  scale_color_fermenter(n.breaks = 7, palette = "RdBu", limits = max(abs(scatter_data$change))*c(-1, 1)) +
  labs(x = "Probability of increase (14 days ahead)", y = "Current admissions (7-day average)",
       title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       subtitle = "Ensemble model",
       col = "Forecast\nchange") +
  theme_bw()

```

### Forecast increase, maps

```{r}

loc <- readRDS(file = here::here("data", "out", "trust_characteristics", "trust_locations.rds"))

loc_sf <- sf::st_as_sf(loc %>% filter(!is.na(lng)), coords = c("lng", "lat"),
                       crs = 4326, agr = "constant", remove = FALSE) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::left_join(current_forecast_tb, by = "id") %>%
  dplyr::filter(!is.na(p_7), !is.na(p_14))

cities <- readr::read_csv(file = "~/Downloads/gb.csv") %>%
  dplyr::filter(!city %in% c("Glasgow")) %>%
  dplyr::slice_head(n = 11) %>%
  dplyr::mutate(label_name = ifelse(city == "Birstall", admin_name, city))

cities_sf <- sf::st_as_sf(cities, coords = c("lng", "lat"), crs = 4326, agr = "constant", remove = FALSE)

# England
covid19.nhs.data::england_utla_shape %>%
  ggplot() +
  geom_sf(lwd = 0.3, col = "grey40", fill = "grey65") +
  # geom_sf(data = cities_sf, col = "grey20", shape = 15, size = 3) +
  geom_sf(data = loc_sf, aes(col = p_14)) +
  geom_sf_text(data = cities_sf, aes(label = label_name)) +
  scale_color_distiller(palette = "PiYG", limits = c(0, 1)) +
  labs(x = "", y = "",
       title = "England",
       col = "Prob. of\nincrease") +
  theme_bw() +
  theme(legend.position = "right")

# London
covid19.nhs.data::england_utla_shape %>%
  ggplot() +
  geom_sf(lwd = 0.3, col = "grey40", fill = "grey65") +
  geom_sf(data = loc_sf, aes(col = p_7), size = 3) +
  coord_sf(xlim = c(-0.5, 0.5), ylim = c(51.3, 51.7), crs = 4326, expand = FALSE) +
  scale_color_distiller(palette = "PiYG", limits = c(0, 1)) +
  labs(x = "", y = "",
       title = "London",
       col = "Prob. of\nincrease") +
  theme_bw() +
  theme(legend.position = "right")

# North West
covid19.nhs.data::england_utla_shape %>%
  ggplot() +
  geom_sf(lwd = 0.3, col = "grey40", fill = "grey65") +
  # geom_sf(data = cities_sf, col = "grey20", shape = 15, size = 3) +
  geom_sf(data = loc_sf, aes(col = p_14), size = 3) +
  geom_sf_text(data = cities_sf, aes(label = label_name)) +
  coord_sf(xlim = c(-3.5, -1), ylim = c(53, 54), crs = 4326, expand = FALSE) +
  scale_color_distiller(palette = "PiYG", limits = c(0, 1)) +
  labs(x = "", y = "",
       title = "North West",
       col = "Prob. of\nincrease") +
  theme_bw() +
  theme(legend.position = "right")

```



## Trusts, by NHS region {.tabset .tabset-pills}

Note: for clarity, we only show forecasts for Trusts which have admitted five or more patients in the last 7 days.

### East of England

```{r}

plots <- return_region_plots(region = "East of England")

plots$current_forecast
plots$scatter

```

### London

```{r}

plots <- return_region_plots(region = "London")

plots$current_forecast
plots$scatter

```

### Midlands

```{r}

plots <- return_region_plots(region = "Midlands")

plots$current_forecast
plots$scatter

```

### North East and Yorkshire

```{r}

plots <- return_region_plots(region = "North East and Yorkshire")

plots$current_forecast
plots$scatter

```

### North West

```{r}

plots <- return_region_plots(region = "North West")

plots$current_forecast
plots$scatter

```

### South East

```{r}

plots <- return_region_plots(region = "South East")

plots$current_forecast
plots$scatter

```

### South West

```{r}

plots <- return_region_plots(region = "South West")

plots$current_forecast
plots$scatter

```


## National and regional {.tabset .tabset-pills}

We derive forecasts of national and regional hospital admissions from the Trust-level admissions. For each of the individual models, the forecast samples are summed to get national/regional forecasts, then summarised into quantile forecasts, and then the ensemble forecast created. These are compared below to forecasts made using EpiNow2.

### National (England)

```{r}

# en2 <- read_csv(file = here::here("current_forecasts",
#                                   "data",
#                                   "admissions_region",
#                                   paste0("epinow2_admisssions_", forecast_date, ".csv"))) %>%
#   filter(type == "forecast",
#          !region %in% c("Northern Ireland", "Scotland", "Wales", "United Kingdom")) %>%
#   dplyr::mutate(forecast_from = forecast_date,
#                 model = "EpiNow2",
#                 horizon = as.integer(date - forecast_date)) %>%
#   select(forecast_from, model, id = region, date, horizon, median, lower_90, lower_50, upper_50, upper_90)

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 28,
                                      date <= forecast_date) %>%
                        dplyr::group_by(date) %>%
                        dplyr::summarise(observed = sum(adm, na.rm = TRUE)) %>%
                        dplyr::mutate(id = "England"),
                      forecast = region_forecast %>%
                        # dplyr::bind_rows(en2) %>%
                        dplyr::filter(id == "England",
                                      horizon <= 14),
                     trusts = "England",
                     trust_facet_var = "id",
                     # models = c("mean_ensemble"),
                     models = c("mean_ensemble", "EpiNow2"),
                     facet_models = TRUE) +
  scale_x_date(breaks = "1 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  labs(title = "England",
       subtitle = "Ensemble model",
       caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data
  geom_line(data = admissions %>%
                        dplyr::filter(date >= forecast_date) %>%
                        dplyr::group_by(date) %>%
                        dplyr::summarise(observed = sum(adm, na.rm = TRUE)) %>%
                        dplyr::mutate(id = "England"),
            aes(x = date, y = observed), lty = 2)

```


### Regional

```{r}

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 28,
                                      date <= forecast_date) %>%
                        dplyr::group_by(nhs_region, date) %>%
                        dplyr::summarise(observed = sum(adm, na.rm = TRUE)) %>%
                        dplyr::rename(id = nhs_region),
                      forecast = region_forecast %>%
                        # dplyr::bind_rows(en2) %>%
                        dplyr::filter(id != "England",
                                      horizon <= 14),
                     trusts = setdiff(unique(region_forecast$id), "England"),
                     trust_facet_var = "id",
                     facet_col = 3,
                     # models = c("mean_ensemble"),
                     models = c("mean_ensemble", "EpiNow2"),
                     facet_models = TRUE) +
  scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  labs(title = "NHS regions",
       subtitle = "Ensemble model",
       caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data
  geom_line(data = admissions %>%
                        dplyr::filter(date >= forecast_date) %>%
                        dplyr::group_by(nhs_region, date) %>%
                        dplyr::summarise(observed = sum(adm, na.rm = TRUE)) %>%
                        dplyr::mutate(id = nhs_region),
            aes(x = date, y = observed), lty = 2)

```

## Focus Trusts {.tabset .tabset-pills}

We compare last weeks forecasts (from `r format.Date(forecast_date - 7, format = "%d %B %Y")`) to the current observed data.

```{r, eval = FALSE}

focus_trusts <- scatter_data %>%
  arrange(-p_14, -change) %>%
  slice_head(n = 5) %>%
  unique() %>%
  pull(id)

focus_forecast <- readRDS(file = here::here("current_forecasts",
                                            "data",
                                            "admissions_trust",
                                            paste0("admissions_", forecast_date - 7, ".rds"))) %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90) %>%
  dplyr::filter(horizon <= 14) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))

```

### Current week
```{r, eval = FALSE}

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 28,
                                      date <= forecast_date) %>%
                        dplyr::rename(observed = adm),
                      forecast = current_forecast,
                      trusts = focus_trusts,
                      models = c("ts_ensemble", "convolution_rt"),
                      facet_models = TRUE) +
  scale_x_date(breaks = "1 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  scale_color_manual(values = c(col_timeser, col_convoln)) +
  scale_fill_manual(values = c(col_timeser, col_convoln)) +
  labs(title = "Top 5 Trusts with biggest forecast probability of increase",
       subtitle = "Time series ensemble and case-convolution",
       caption = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data (dashed)
  geom_line(data = admissions %>%
                        dplyr::filter(id %in% focus_trusts,
                                      date >= forecast_date) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed), lty = 2)

```

### Last week
```{r, eval = FALSE}

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 7 - 28,
                                      date <= forecast_date - 7) %>%
                        dplyr::rename(observed = adm),
                      forecast = focus_forecast,
                      trusts = focus_trusts,
                      models = c("ts_ensemble", "convolution_rt"),
                      facet_models = TRUE) +
  scale_x_date(breaks = "1 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  scale_color_manual(values = c(col_timeser, col_convoln)) +
  scale_fill_manual(values = c(col_timeser, col_convoln)) +
  labs(title = "Top 5 Trusts with biggest forecast probability of increase",
       subtitle = "Time series ensemble and case-convolution",
       caption = paste0("Forecasts from ", format.Date(forecast_date - 7, format = "%d %B %Y"))) +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data (dashed)
  geom_line(data = admissions %>%
                        dplyr::filter(id %in% focus_trusts,
                                      date >= forecast_date - 7) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed), lty = 2)

```



# Past forecasts {.tabset}

```{r, include = FALSE}
plot_dates <- unique(all_reg_forecasts$forecast_from)[which(unique(all_reg_forecasts$forecast_from) < forecast_date - 7 & unique(all_reg_forecasts$forecast_from) > forecast_date - 42)]
```

## Trusts, all regions

```{r, eval = FALSE}

plot_forecast_bars(observed = admissions %>%
                       dplyr::filter(date >= forecast_date - 42) %>%
                       dplyr::rename(observed = adm),
                   forecast = all_forecasts,
                   h = 14,
                   use_dates = plot_dates,
                   trusts = plot_trusts_observed,
                   models = "mean_ensemble",
                   facet_models = FALSE) +
  scale_x_date(limits = c(forecast_date - 42, forecast_date + 1),
               breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
    labs(title = "Top 25 Trusts with most admissions in last 28 days",
       subtitle = "Past 14-day ahead forecasts, ensemble model") +
  theme(legend.position = "none")

plot_forecast_bars(observed = admissions %>%
                       dplyr::filter(date >= forecast_date - 42) %>%
                       dplyr::rename(observed = adm),
                   forecast = all_forecasts,
                   h = 14,
                   use_dates = plot_dates,
                   trusts = plot_trusts_observed,
                   models = "convolution_rt",
                   facet_models = FALSE) +
  scale_x_date(limits = c(forecast_date - 42, forecast_date + 1),
               breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
  scale_color_manual(values = c(col_convoln)) +
  scale_fill_manual(values = c(col_convoln)) +
    labs(title = "Top 25 Trusts with most admissions in last 28 days",
       subtitle = "Past 14-day ahead forecasts, case-convolution model") +
  theme(legend.position = "none")

```

## National

We derive forecasts of national hospital admissions from the Trust-level admissions. For each of the individual models, the forecast samples are summed to get national forecasts, then summarised into quantile forecasts. The ensemble forecast is created from the national quantile forecasts.


```{r, eval = FALSE, fig.width = 14, fig.height = 6}

region_obs <- admissions %>%
  dplyr::group_by(nhs_region, date) %>%
  dplyr::summarise(observed = sum(adm, na.rm = TRUE)) %>%
  dplyr::rename(id = nhs_region) %>%
  dplyr::bind_rows(admissions %>%
                     dplyr::group_by(date) %>%
                     dplyr::summarise(observed = sum(adm, na.rm = TRUE)) %>%
                     dplyr::mutate(id = "England")) %>%
  dplyr::filter(date >= forecast_date - 42)

plot_forecast_bars(observed = region_obs,
                   forecast = all_reg_forecasts,
                   h = 14,
                   use_dates = plot_dates,
                   trusts = "England",
                   trust_facet_var = "id",
                   models = c("convolution_rt", "mean_ensemble"),
                   facet_models = TRUE) +
  scale_x_date(limits = c(forecast_date - 42, forecast_date + 1),
               breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
  scale_color_manual(values = c(col_convoln, col_ensemble)) +
  scale_fill_manual(values = c(col_convoln, col_ensemble)) +
    labs(title = "National",
       subtitle = "Past 14-day ahead forecasts") +
  theme(legend.position = "none")

```

## Regional

We derive forecasts of regional hospital admissions from the Trust-level admissions. For each of the individual models, the forecast samples are summed to get regional forecasts, then summarised into quantile forecasts. The ensemble forecast is created from the regional quantile forecasts.


```{r, eval = FALSE}

plot_forecast_bars(observed = region_obs,
                   forecast = all_reg_forecasts,
                   h = 14,
                   use_dates = plot_dates,
                   trusts = setdiff(unique(region_forecast$id), "England"),
                   trust_facet_var = "id",
                   models = c("convolution_rt", "mean_ensemble"),
                   facet_models = TRUE) +
  scale_x_date(limits = c(forecast_date - 42, forecast_date + 1),
               breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
  scale_color_manual(values = c(col_convoln, col_ensemble)) +
  scale_fill_manual(values = c(col_convoln, col_ensemble)) +
    labs(title = "NHS regions",
       subtitle = "Past 14-day ahead forecasts") +
  theme(legend.position = "none")

```


