---
title: "Trust-level Covid-19 hospital admissions forecasts"
author: "Sophie Meakin, Sam Abbott, Seb Funk"
date: "`r format.Date(Sys.Date(), format = '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(ggrepel)
library(patchwork)
source(here::here("R", "load_data_fns.R"))
source(here::here("R", "plot_fns.R"))
source(here::here("R", "utils.R"))

forecast_date <- as.Date("2021-05-16")
utla_names <- c("Bolton",
                "Blackburn with Darwen",
                "Bedford")

```

```{r observed, include = FALSE}

admissions <- load_hospital_data(keep_data = c("all_adm"), add_private = TRUE) %>%
  dplyr::rename(adm = all_adm) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))

dat <- load_combined_data() %>%
  dplyr::filter(date >= as.Date("2021-02-01"),
                date < max(date)) %>%
  dplyr::rename(adm = all_adm, occ = bed_occ) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  tidyr::pivot_longer(cols = c(cases, adm, occ)) %>%
  dplyr::filter(name != "occ") %>%
  dplyr::mutate(id = trust_name,
                name = ifelse(name == "cases", "Cases", "Admissions")) %>%
  dplyr::select(-trust_name, -nhs_region) %>%
  na.omit()

plot_trusts_observed <- admissions %>%
  dplyr::filter(date > forecast_date - 28,
                date <= forecast_date) %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(total_adm = sum(adm, na.rm = TRUE)) %>%
  dplyr::arrange(-total_adm) %>%
  dplyr::slice_head(n = 25) %>%
  dplyr::pull(id)

 trusts_observed7 <- admissions %>%
  dplyr::filter(date > forecast_date - 7,
                date <= forecast_date) %>%
  dplyr::group_by(nhs_region, id) %>%
  dplyr::summarise(observed = mean(adm, na.rm = TRUE))

```

# Summary

The current forecast date is **`r format.Date(forecast_date, format = "%d %B")`**, showing data until **`r format.Date(max(admissions$date, na.rm = TRUE), format = "%d %B")`**.

The forecasting model is an unweighted ensemble of three individual models:

1. unweighted time series ensemble model (autoregressive ARIMA, ETS and naive models)
2. regression + 7-day-lagged cases (cases mapped from UTLA to Trust using Trust-UTLA mapping in `covid19.nhs.data`)
3. convolution from cases to admissions (scaled; cases mapped to Trusts as above)

All models are trained on the last 6 weeks of data (from `r format.Date(forecast_date - 42, format = "%d %B")`) and forecasts are made for the following 14 days. 


# Current forecast

```{r load forecasts}

# Load forecast summary
current_forecast <- readRDS(file = here::here("current_forecasts",
                                              "admissions_trust",
                                              paste0("admissions_", forecast_date, ".rds"))) %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90) %>%
  dplyr::filter(horizon <= 14) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))

forecast_point <- current_forecast %>%
  dplyr::filter(model == "mean_ensemble",
                horizon %in% c(7, 14)) %>%
  dplyr::select(id, horizon, median) %>%
  dplyr::mutate(horizon = paste0("forecast_", horizon)) %>%
  tidyr::pivot_wider(id_cols = id, names_from = horizon, values_from = median) %>%
  dplyr::left_join(trusts_observed7, by = "id") %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::select(nhs_region, id, trust_name, observed, forecast_7, forecast_14)


# Load forecast samples
current_forecast_long <- readRDS(file = here::here("current_forecasts",
                                              "admissions_trust",
                                              paste0("admissions_long_", forecast_date, ".rds")))

forecast_prob <- current_forecast_long %>%
  dplyr::filter(model == "mean_ensemble",
                horizon %in% c(7, 14)) %>%
  dplyr::left_join(trusts_observed7, by = c("id")) %>%
  dplyr::mutate(observed = round(observed)) %>%
  dplyr::group_by(forecast_from, id, horizon) %>%
  dplyr::filter(value > observed) %>%
  dplyr::group_by(forecast_from, id, horizon) %>%
  dplyr::filter(quantile == min(quantile)) %>%
  dplyr::mutate(horizon = paste0("p_", horizon),
                p_increase = 1-quantile) %>%
  dplyr::ungroup() %>%
  dplyr::select(id, horizon, p_increase) %>%
  unique() %>%
  tidyr::pivot_wider(id_cols = -c(horizon, p_increase), names_from = horizon, values_from = p_increase)

current_forecast_tb <- forecast_point %>%
  dplyr::left_join(forecast_prob, by = "id") %>%
  dplyr::select(nhs_region, id, trust_name, observed, forecast_7, p_7, forecast_14, p_14) %>%
  dplyr::mutate(observed = round(observed, 1),
                p_7 = round(p_7, 2),
                p_14 = round(p_14, 2))

plot_trusts_forecast <- current_forecast_tb %>%
  # dplyr::filter(forecast_7 - observed >= 0) %>%
  dplyr::arrange(-(forecast_7 - observed)) %>%
  dplyr::ungroup() %>%
  dplyr::slice_head(n = 25) %>%
  dplyr::pull(id)

```


## By recent observed admissions

```{r plot current forecasts (top observed), fig.width=14, fig.height=7}

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 42,
                                      date <= forecast_date) %>%
                        dplyr::rename(observed = adm),
                      forecast = current_forecast,
                     trusts = plot_trusts_observed,
                     models = "mean_ensemble",
                     facet_models = FALSE) +
  scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  labs(title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       subtitle = "Top 25 Trusts with most admissions in last 28 days") +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data
  geom_line(data = admissions %>%
                        dplyr::filter(id %in% plot_trusts_observed,
                                      date >= forecast_date) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed))

```


## By forecast admissions

```{r plot current forecasts (top forecast), fig.width=14, fig.height=7}

plot_forecast_ribbons(observed = admissions %>%
                        dplyr::filter(date > forecast_date - 42,
                                      date <= forecast_date) %>%
                        dplyr::rename(observed = adm),
                     forecast = current_forecast,
                     trusts = plot_trusts_forecast,
                     models = "mean_ensemble",
                     facet_models = FALSE) +
  scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
  labs(title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       subtitle = "Top 25 Trusts with biggest forecast increase in admissions") +
  theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
  ## Adding current observed data
  geom_line(data = admissions %>%
                        dplyr::filter(id %in% plot_trusts_forecast,
                                      date >= forecast_date) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed))

```



```{r table current forecats}

DT::datatable(data = current_forecast_tb %>%
                dplyr::select(ID = id,
                              Name = trust_name,
                              `Current 7-day average` = observed,
                              `One-week ahead forecast` = forecast_7,
                              `Probability of increase (7 days)` = p_7,
                              `Two-weeks ahead forecast` = forecast_14,
                              `Probability of increase (14 days)` = p_14),
              rownames = FALSE,
              )

```

## Probability of increase (scatter)
```{r admissions vs probability, fig.width=14, fig.height=7}

scatter_data <- current_forecast_tb %>%
  dplyr::ungroup() %>%
  dplyr::mutate(change = forecast_14 - observed,
                label = ifelse(observed > quantile(observed, 0.95, na.rm = TRUE) |
                                 p_14 > quantile(p_14, 0.95, na.rm = TRUE),
                               trust_name, NA),
                label = stringr::str_wrap(label, width = 25))

scatter_data %>%
  ggplot(aes(x = p_14, y = observed, col = change)) +
  geom_point(size = 3) +
  geom_text_repel(aes(label = label), size = 3, col = "grey20",
                  point.padding = 0.2, min.segment.length = 0.1) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 20, 2)) +
  scale_color_fermenter(n.breaks = 7, palette = "RdBu", limits = max(abs(scatter_data$change))*c(-1, 1)) +
  labs(x = "Probability of increase (14 days ahead)", y = "Current admissions (7-day average)",
       title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       col = "Forecast\nchange") +
  theme_bw()

# Facetted by NHS region
scatter_data %>%
  ggplot(aes(x = p_14, y = observed, col = change)) +
  geom_point(size = 3) +
  geom_text_repel(aes(label = label), size = 3, col = "grey20",
                  point.padding = 0.2, min.segment.length = 0.1) +
  facet_wrap(. ~ nhs_region) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 20, 2)) +
  scale_color_fermenter(n.breaks = 7, palette = "RdBu", limits = max(abs(scatter_data$change))*c(-1, 1)) +
  labs(x = "Probability of increase (14 days ahead)", y = "Current admissions (7-day average)",
       title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       col = "Forecast\nchange") +
  theme_bw()

```

## Probability of increase (map)
```{r map probability increase, fig.width=14, fig.height=7}

loc <- readRDS(file = here::here("data", "out", "trust_characteristics", "trust_locations.rds"))

loc_sf <- sf::st_as_sf(loc %>% filter(!is.na(lng)), coords = c("lng", "lat"),
                       crs = 4326, agr = "constant", remove = FALSE) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::left_join(current_forecast_tb, by = "id") %>%
  dplyr::filter(!is.na(p_7), !is.na(p_14))

cities <- readr::read_csv(file = "~/Downloads/gb.csv") %>%
  dplyr::filter(!city %in% c("Glasgow")) %>%
  dplyr::slice_head(n = 11) %>%
  dplyr::mutate(label_name = ifelse(city == "Birstall", admin_name, city))

cities_sf <- sf::st_as_sf(cities, coords = c("lng", "lat"), crs = 4326, agr = "constant", remove = FALSE)

# England
covid19.nhs.data::england_utla_shape %>%
  ggplot() +
  geom_sf(lwd = 0.3, col = "grey40", fill = "grey65") +
  # geom_sf(data = cities_sf, col = "grey20", shape = 15, size = 3) +
  geom_sf(data = loc_sf, aes(col = p_14)) +
  geom_sf_text(data = cities_sf, aes(label = label_name)) +
  scale_color_distiller(palette = "PiYG", limits = c(0, 1)) +
  labs(x = "", y = "",
       title = "England",
       col = "Prob. of\nincrease") +
  theme_bw() +
  theme(legend.position = "right")

# London
covid19.nhs.data::england_utla_shape %>%
  ggplot() +
  geom_sf(lwd = 0.3, col = "grey40", fill = "grey65") +
  geom_sf(data = loc_sf, aes(col = p_7), size = 3) +
  coord_sf(xlim = c(-0.5, 0.5), ylim = c(51.3, 51.7), crs = 4326, expand = FALSE) +
  scale_color_distiller(palette = "PiYG", limits = c(0, 1)) +
  labs(x = "", y = "",
       title = "London",
       col = "Prob. of\nincrease") +
  theme_bw() +
  theme(legend.position = "right")

# North West
covid19.nhs.data::england_utla_shape %>%
  ggplot() +
  geom_sf(lwd = 0.3, col = "grey40", fill = "grey65") +
  # geom_sf(data = cities_sf, col = "grey20", shape = 15, size = 3) +
  geom_sf(data = loc_sf, aes(col = p_14), size = 3) +
  geom_sf_text(data = cities_sf, aes(label = label_name)) +
  coord_sf(xlim = c(-3.5, -1), ylim = c(53, 54), crs = 4326, expand = FALSE) +
  scale_color_distiller(palette = "PiYG", limits = c(0, 1)) +
  labs(x = "", y = "",
       title = "North West",
       col = "Prob. of\nincrease") +
  theme_bw() +
  theme(legend.position = "right")

```


# Past forecasts

```{r load past forecasts}

file_dir <- here::here("current_forecasts", "admissions_trust")
file_names <- list.files(file_dir)[which(!grepl("latest", list.files(file_dir)) &
                                           !grepl("long", list.files(file_dir)) &
                                           !grepl(forecast_date, list.files(file_dir)))]

all_forecasts <- purrr::map_df(.x = file_names, .f = ~ {
  
  out <- readRDS(file = here::here(file_dir, .x))
  return(out)
  
}) %>%
  dplyr::bind_rows() %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(trust_name = stringr::str_wrap(trust_name, width = 40))

```

```{r plot past forecasts, fig.width=14, fig.height=7}

plot_forecast_bars(observed = admissions %>%
                       dplyr::filter(date >= forecast_date - 84) %>%
                       dplyr::rename(observed = adm),
                   forecast = all_forecasts,
                   h = 7,
                   trusts = plot_trusts_observed,
                   models = "mean_ensemble",
                   facet_models = FALSE) +
  scale_x_date(limits = c(forecast_date - 63, forecast_date + 1),
               breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
  labs(subtitle = "Top 25 Trusts with most admissions in last 28 days") +
  theme(legend.position = "none")

plot_forecast_bars(observed = admissions %>%
                       dplyr::filter(date >= forecast_date - 84) %>%
                       dplyr::rename(observed = adm),
                   forecast = all_forecasts,
                   h = 14,
                   trusts = plot_trusts_observed,
                   models = "mean_ensemble",
                   facet_models = FALSE) +
  scale_x_date(limits = c(forecast_date - 63, forecast_date + 1),
               breaks = "2 weeks", date_labels = "%d %b") +
  scale_y_continuous(limits = c(0, NA), breaks = integer_breaks()) +
  labs(subtitle = "Top 25 Trusts with most admissions in last 28 days") +
  theme(legend.position = "none")

```


# Areas of interest

Below is more detailed information about potential Trusts of interest, defined as Trusts where more than 20% of patients are admitted from one of the following UTLAs: **`r paste0(utla_names, collapse = ", ")`**.

```{r area of interest, fig.width=14, fig.height=7}

focus_trust <- covid19.nhs.data::get_names(covid19.nhs.data::trust_utla_mapping) %>%
  dplyr::filter(geo_name %in% utla_names,
                p_geo > 0.2) %>%
  dplyr::arrange(geo_name)

for(use_id in unique(focus_trust$trust_code)){
  
  trust_name <- focus_trust %>%
    dplyr::filter(trust_code == use_id) %>%
    dplyr::pull(trust_name) %>%
    unique()
  
  utla_names <- focus_trust %>%
    dplyr::filter(trust_code == use_id) %>%
    dplyr::pull(geo_name) %>%
    unique()
  
  plot_title <- paste0(trust_name,
                       " (UTLA: ",
                       paste0(utla_names, collapse = ", "),
                       ")")
  
  g_observed <- plot_observed(observed = dat, trusts = trust_name,
                              plot_vars = c("Cases", "Admissions"), plot_raw = TRUE) +
     annotate("rect", xmin = forecast_date - 42, xmax = forecast_date, ymin = -Inf, ymax = Inf, alpha = 0.2) +
    scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
    labs(title = plot_title,
         subtitle = "Trust-level cases (estimated) and hospital admissions (observed)") +
    theme(legend.position = "bottom")

  g_forecast <- plot_forecast_ribbons(observed = admissions %>%
                                        dplyr::filter(date > forecast_date - 42,
                                                      date <= forecast_date) %>%
                                        dplyr::rename(observed = adm),
                                      forecast = current_forecast,
                                      trusts = use_id,
                                      models = c("ts_ensemble", "regression_arima", "convolution_rt", "mean_ensemble"),
                                      facet_models = TRUE) +
    scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
    scale_y_continuous(breaks = integer_breaks(), limits = c(0, NA)) +
    labs(subtitle = paste0("Hospital admissions forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
    theme(legend.position = "none", strip.text.x = element_text(size = 8)) +
    geom_line(data = admissions %>%
                        dplyr::filter(id %in% use_id,
                                      date >= forecast_date) %>%
                        dplyr::rename(observed = adm),
            aes(x = date, y = observed))

  g_out <- g_observed | g_forecast
  
  print(g_out)
  
}

```


# Case-hospitalisation ratio

```{r case-hosp ratio, fig.width=14, fig.height=7}

convolution_chr <- readRDS(file = here::here("current_forecasts",
                                           "chr",
                                           paste0("chr_", forecast_date, ".rds")))

trusts_observed7 %>%
  dplyr::left_join(convolution_chr %>%
                     dplyr::select(id, median, lwr = lower_90, upr = upper_90), by = "id") %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::mutate(label = ifelse(observed > quantile(observed, 0.95) |
                                 median > quantile(median, 0.95, na.rm = TRUE) |
                                 id %in% focus_trust$trust_code,
                               trust_name,
                               NA),
                label = stringr::str_wrap(label, width = 25)) %>%
  ggplot() +
  geom_point(aes(x = median, y = observed), size = 3, alpha = 0.5) +
  geom_segment(aes(x = lwr, xend = upr, y = observed, yend = observed), lwd = 1, alpha = 0.5) +
  geom_text_repel(aes(x = median, y = observed, label = label), size = 3, col = "grey20",
                  point.padding = 0.2, min.segment.length = 0.1) +
  facet_wrap(. ~ nhs_region) +
  scale_x_continuous(limits = c(0, 0.3)) +
  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 20, 2)) +
  labs(x = "Case-hospitalisation ratio",
       y = "Current admissions (7-day average)",
       title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y"))) +
  theme_bw()

```