---
title: "Trust-level Covid-19 admissions forecasts"
author: "Sophie Meakin"
date: "`r format.Date(Sys.Date(), format = '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
source(here::here("R", "load_data.R"))
source(here::here("R", "plot_forecasts.R"))

today_date <- as.Date("2021-03-19")
forecast_date <- lubridate::floor_date(today_date, unit = "week", week_start = 7)

```

```{r observed}

admissions <- load_hospital_data(keep_data = c("all_adm", "new_adm"))

plot_trusts <- admissions %>%
  dplyr::filter(date > forecast_date - 28) %>%
  dplyr::group_by(id) %>%
  dplyr::summarise(total_adm = sum(new_adm, na.rm = TRUE)) %>%
  dplyr::arrange(-total_adm) %>%
  dplyr::slice_head(n = 25) %>%
  dplyr::pull(id)

```

# Summary

The current forecast date is **`r format.Date(forecast_date, format = "%d %B")`**.

The forecasting model is an unweighted ensemble of three individual models:

1. unweighted time series ensemble model (autoregressive ARIMA, ETS, TBATS and naive models)
2. regression + 7-day-lagged cases (cases mapped from UTLA to Trust using Trust-UTLA mapping in `covid19.nhs.data`)
3. convolution from cases to admissions (scaled; cases mapped to Trusts as above)

All models are trained on the last 6 weeks of data (from `r format.Date(forecast_date - 42, format = "%d %B")`) and forecasts are made for the following 14 days. 


# Current forecast

```{r load forecasts}

file_name <- here::here("current_forecasts", "admissions_trust", "admissions_latest.rds")

current_forecast <- readRDS(file = file_name) %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90)

```

```{r plot current forecasts, fig.width=16, fig.height=9}

plot_forecast_ribbons(observed = admissions %>%
                       dplyr::filter(date >= as.Date("2021-02-01")) %>%
                       dplyr::select(id, date, observed = all_adm),
                     forecast = current_forecast,
                     trusts = plot_trusts,
                     models = "mean_ensemble",
                     facet_models = FALSE) +
  scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
  labs(title = paste0("Forecasts from ", format.Date(forecast_date, format = "%d %B %Y")),
       subtitle = "Top-25 Trusts with highest admissions in last 28 days") +
  theme(legend.position = "none")

```

```{r table current forecats}

admissions %>%
  dplyr::filter(date > forecast_date - 7) %>%
  dplyr::select(id, date, adm = all_adm) %>%
  dplyr::bind_rows(current_forecast %>%
                     dplyr::filter(model == "mean_ensemble") %>%
                     dplyr::select(id, date, adm = median, upper_50, upper_90)) %>%
  dplyr::arrange(id, date) %>%
  dplyr::mutate(week = lubridate::floor_date(date - 1, unit = "week", week_start = 7) + 7,
                week = case_when(week == forecast_date ~ "current_week",
                                 week == forecast_date + 7 ~ "one_week",
                                 week == forecast_date + 14 ~ "two_weeks"),
                week = ordered(week, c("current_week", "one_week", "two_weeks"))) %>%
  dplyr::group_by(id, week) %>%
  dplyr::summarise(adm = sum(adm, na.rm = TRUE)) %>%
  tidyr::pivot_wider(id_cols = id, names_from = week, values_from = adm) %>%
  dplyr::left_join(covid19.nhs.data::trust_names, by = c("id" = "trust_code")) %>%
  dplyr::arrange(id) %>%
  dplyr::select(ID = id, Name = trust_name, `Last week` = current_week, `One-week ahead forecast` = one_week, `Two-weeks ahead forecast` = two_weeks) %>%
  kableExtra::kbl() %>%
  kableExtra::kable_styling()

```


# Past forecasts

```{r load past forecasts}

file_dir <- here::here("current_forecasts", "admissions_trust")
file_names <- list.files(file_dir)[which(!grepl("latest", list.files(file_dir)))]

all_forecasts <- purrr::map_df(.x = file_names, .f = ~ {
  
  out <- readRDS(file = here::here(file_dir, .x))
  return(out)
  
}) %>%
  dplyr::bind_rows() %>%
  dplyr::select(-quantile) %>%
  tidyr::pivot_wider(id_cols = -c(quantile_label, value), names_from = quantile_label) %>%
  dplyr::select(forecast_from, model, id, date = date_horizon, horizon,
                median = lower_0, lower_90, lower_50, upper_50, upper_90)

```

```{r plot past forecasts, fig.width=16, fig.height=9}

plot_forecast_bars(observed = admissions %>%
                       dplyr::filter(date >= as.Date("2021-02-01")) %>%
                       dplyr::select(id, date, observed = all_adm),
                   forecast = all_forecasts,
                   h = 7,
                   trusts = plot_trusts,
                   models = "mean_ensemble",
                   facet_models = FALSE) +
  scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
  labs(subtitle = "Top-25 Trusts with highest admissions in last 28 days") +
  theme(legend.position = "none")

plot_forecast_bars(observed = admissions %>%
                       dplyr::filter(date >= as.Date("2021-02-01")) %>%
                       dplyr::select(id, date, observed = all_adm),
                   forecast = all_forecasts,
                   h = 14,
                   trusts = plot_trusts,
                   models = "mean_ensemble",
                   facet_models = FALSE) +
  scale_x_date(breaks = "2 weeks", date_labels = "%d %b") +
  labs(subtitle = "Top-25 Trusts with highest admissions in last 28 days") +
  theme(legend.position = "none")

```

