---
title: "Estimate the lag between cases and admissions"
author: "Sophie Meakin"
date: "01/07/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(patchwork)
library(covid19.nhs.data)
library(covidregionaldata)

source(here::here("R", "load_data_fns.R"))
source(here::here("R", "correlation_fns.R"))
source(here::here("R", "utils.R"))

```

# Summary

Estimating the optimal lag between cases and hospital admissions (national and by NHS region) by considering the lag for which the Kendall rank correlation coefficient is maximised.

# Initialise

* define `forecast_dates` (week beginning)
* load raw data
* subset national/regional data

```{r init}

forecast_dates <- as.character(seq.Date(from = as.Date("2020-08-02")+63, to = as.Date("2021-04-25"), by = "week"))
df <- load_combined_data()

```

```{r new vars}

df_nat <- df %>%
  dplyr::filter(date >= as.Date("2020-08-02"),
                date < as.Date("2021-05-02")) %>%
  dplyr::mutate(id = "England") %>%
  dplyr::group_by(id, date) %>%
  dplyr::summarise(all_adm = sum(all_adm, na.rm = TRUE),
                   cases = sum(cases, na.rm = TRUE)) %>%
  dplyr::mutate(adm_trend = round((stl(ts(all_adm, freq = 7), s.window = 7)$time.series)[,2]),
                cases_trend = round((stl(ts(cases, freq = 7), s.window = 7)$time.series)[,2])) %>%
  dplyr::ungroup()

df_reg <- df %>%
    dplyr::filter(date >= as.Date("2020-08-02"),
                date < as.Date("2021-05-02")) %>%
  dplyr::group_by(id = nhs_region, date) %>%
  dplyr::summarise(all_adm = sum(all_adm, na.rm = TRUE),
                   cases = sum(cases, na.rm = TRUE)) %>%
  dplyr::mutate(adm_trend = round((stl(ts(all_adm, freq = 7), s.window = 7)$time.series)[,2]),
                cases_trend = round((stl(ts(cases, freq = 7), s.window = 7)$time.series)[,2])) %>%
  dplyr::ungroup()

```

# Analyses

```{r cross correlation}

corr_nat <- purrr::map_df(.x = forecast_dates, .f = ~{
    
    out <- calc_cor(df = df_nat %>%
                      dplyr::select(id, date, admissions = adm_trend, cases_trend),
                    var = "cases_trend", lags = 0:14, date_end = as.Date(.x)) %>%
      dplyr::mutate(forecast_from = .x)
    
  })

corr_reg <- purrr::map_df(.x = forecast_dates, .f = ~{
    
    out <- calc_cor(df = df_reg %>%
                      dplyr::select(id, date, admissions = adm_trend, cases_trend),
                    var = "cases_trend", lags = 0:14, date_end = as.Date(.x)) %>%
      dplyr::mutate(forecast_from = .x)
    
  })

```

# Output

## Plot combined data
```{r data nat}

# National
g_combined_nat <- df_nat %>%
  dplyr::select(id, date, cases, cases_trend, adm = all_adm, adm_trend) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(adm = adm/sd(adm),
                adm_trend = adm_trend/sd(adm_trend),
                cases = cases/sd(cases),
                cases_trend = cases_trend/sd(cases_trend)) %>%
  tidyr::pivot_longer(cols = -c(id, date)) %>%
  dplyr::mutate(name = ordered(name, c("cases", "cases_trend", "adm", "adm_trend"))) %>%
  ggplot(aes(x = date, y = value, col = name)) +
  geom_line() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  facet_wrap(. ~ id) +
  scale_color_brewer(palette = "Paired") +
  labs(x = "Date", y = "Value (standardised)",
       col = "Data") +
  theme_bw() +
  theme(legend.position = "top")

# By NHS region
g_combined_reg <- df_reg %>%
  dplyr::select(id, date, cases, cases_trend, adm = all_adm, adm_trend) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(adm = adm/sd(adm),
                adm_trend = adm_trend/sd(adm_trend),
                cases = cases/sd(cases),
                cases_trend = cases_trend/sd(cases_trend)) %>%
  tidyr::pivot_longer(cols = -c(id, date)) %>%
  dplyr::mutate(name = ordered(name, c("cases", "cases_trend", "adm", "adm_trend"))) %>%
  dplyr::filter(!is.na(id)) %>%
  ggplot(aes(x = date, y = value, col = name)) +
  geom_line() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  facet_wrap(. ~ id) +
  scale_color_brewer(palette = "Paired") +
  labs(x = "Date", y = "Value (standardised)",
       col = "Data") +
  theme_bw() +
  theme(legend.position = "top")

```

## Cross-correlation, text
```{r cc text}

# National
corr_nat %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr, na.rm = TRUE)) %>%
  dplyr::filter(corr > 0.995*max(corr))

# By NHS region
corr_reg %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr, na.rm = TRUE)) %>%
  dplyr::filter(corr > 0.995*max(corr)) %>%
  dplyr::group_by(id) %>%
  dplyr::filter(lag_days %in% c(max(lag_days), min(lag_days)))

```

## Cross-correlation, tile

```{r cc tile}

g_tile_nat <- corr_nat %>%
  dplyr::filter(lag_days <= 10) %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from)) %>%
  ggplot(aes(x = forecast_from, y = lag_days, fill = corr)) +
  geom_tile() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  scale_y_continuous(breaks = integer_breaks()) +
  scale_fill_distiller(palette = "RdBu", limits = c(-1, 1)) +
  facet_wrap(. ~ id) +
  labs(x = "Forecast date", y = "Lag (days)",
       title = "A",
       fill = "Correlation") +
  theme_bw() +
  theme(legend.position = "none")

g_tile_reg <- corr_reg %>%
  dplyr::filter(lag_days <= 10,
                !is.na(id)) %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from)) %>%
  ggplot(aes(x = forecast_from, y = lag_days, fill = corr)) +
  geom_tile() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  scale_fill_distiller(palette = "RdBu", limits = c(-1, 1)) +
  facet_wrap(. ~ id, ncol = 2) +
  labs(x = "Forecast date", y = "Lag (days)",
       title = "B",
       fill = "Correlation") +
  theme_bw() +
  theme(legend.position = "top")

#####
guide_area() / (g_tile_nat | g_tile_reg) +
  plot_layout(heights = c(0.1, 1), guides = "collect")
#####

```

## Cross-correlation, line

```{r cc line}

g_correlation_nat <- corr_nat %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr)) %>%
  ggplot(aes(x = lag_days, y = corr)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  scale_y_continuous(limits = c(0.5, 1)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Lag (days)", y = "Correlation",
       col = "NHS region",
       title = "A") +
  theme_bw()

g_correlation_reg <- corr_reg %>%
  dplyr::filter(!is.na(id)) %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr)) %>%
  ggplot(aes(x = lag_days, y = corr)) +
  geom_line(aes(col = id), lwd = 0.6) +
  geom_line(data = corr_reg %>%
              dplyr::filter(!is.na(id)) %>%
              dplyr::group_by(lag_days) %>%
              dplyr::summarise(corr = mean(corr)), lwd = 0.6, lty = 2) +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  scale_y_continuous(limits = c(0.5, 1)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Lag (days)", y = "",
       col = "NHS region",
       title = "B") +
  theme_bw()

#####
g_correlation_nat | g_correlation_reg
#####

ggsave(filename = here::here("data", "out", "figures", "figure_s3.png"),
       width = 14, height = 8, units = "in",
       dpi = 500)

```

