---
title: "Estimate the lag between cases and admissions"
author: "Sophie Meakin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(patchwork)

source(here::here("R", "load_data.R"))
source(here::here("R", "correlation_fns.R"))
source(here::here("R", "utils.R"))

```

# Summary

Estimating the optimal lag between cases and hospital admissions (national and by NHS region) by considering the lag for which the Kendall rank correlation coefficient is maximised.

# Initialise

* define `forecast_dates` (week beginning)
* load raw data
* subset national/regional data

```{r init}

forecast_dates <- as.character(seq.Date(from = as.Date("2020-08-02")+63, by = "week", length = 18))
df <- load_combined_data()

```

```{r new vars}

df_nat <- df %>%
  dplyr::filter(date >= as.Date("2020-08-02"),
                date < as.Date("2021-02-01")) %>%
  dplyr::mutate(id = "England") %>%
  dplyr::group_by(id, date) %>%
  dplyr::summarise(all_adm = sum(all_adm, na.rm = TRUE),
                   cases = sum(cases, na.rm = TRUE)) %>%
  dplyr::mutate(adm_trend = round((stl(ts(all_adm, freq = 7), s.window = 7)$time.series)[,2]),
                cases_trend = round((stl(ts(cases, freq = 7), s.window = 7)$time.series)[,2])) %>%
  dplyr::ungroup()

df_reg <- df %>%
    dplyr::filter(date >= as.Date("2020-08-02"),
                date < as.Date("2021-02-01")) %>%
  dplyr::group_by(id = nhs_region, date) %>%
  dplyr::summarise(all_adm = sum(all_adm, na.rm = TRUE),
                   cases = sum(cases, na.rm = TRUE)) %>%
  dplyr::mutate(adm_trend = round((stl(ts(all_adm, freq = 7), s.window = 7)$time.series)[,2]),
                cases_trend = round((stl(ts(cases, freq = 7), s.window = 7)$time.series)[,2])) %>%
  dplyr::ungroup()

```

# Analyses

```{r cross correlation}

corr_nat <- purrr::map_df(.x = forecast_dates, .f = ~{
    
    out <- calc_cor(df = df_nat %>%
                      dplyr::select(id, date, admissions = adm_trend, cases_trend),
                    var = "cases_trend", lags = 0:14, date_end = as.Date(.x)) %>%
      dplyr::mutate(forecast_from = .x)
    
  })

corr_reg <- purrr::map_df(.x = forecast_dates, .f = ~{
    
    out <- calc_cor(df = df_reg %>%
                      dplyr::select(id, date, admissions = adm_trend, cases_trend),
                    var = "cases_trend", lags = 0:14, date_end = as.Date(.x)) %>%
      dplyr::mutate(forecast_from = .x)
    
  })

```

# Output

## Plot combined data
```{r data nat}

# National
g_combined_nat <- df_nat %>%
  dplyr::select(id, date, cases, cases_trend, adm = all_adm, adm_trend) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(adm = adm/sd(adm),
                adm_trend = adm_trend/sd(adm_trend),
                cases = cases/sd(cases),
                cases_trend = cases_trend/sd(cases_trend)) %>%
  tidyr::pivot_longer(cols = -c(id, date)) %>%
  dplyr::mutate(name = ordered(name, c("cases", "cases_trend", "adm", "adm_trend"))) %>%
  ggplot(aes(x = date, y = value, col = name)) +
  geom_line() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  facet_wrap(. ~ id) +
  scale_color_brewer(palette = "Paired") +
  labs(x = "Date", y = "Value (standardised)",
       col = "Data") +
  theme_bw() +
  theme(legend.position = "top")

# By NHS region
g_combined_reg <- df_reg %>%
  dplyr::select(id, date, cases, cases_trend, adm = all_adm, adm_trend) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(adm = adm/sd(adm),
                adm_trend = adm_trend/sd(adm_trend),
                cases = cases/sd(cases),
                cases_trend = cases_trend/sd(cases_trend)) %>%
  tidyr::pivot_longer(cols = -c(id, date)) %>%
  dplyr::mutate(name = ordered(name, c("cases", "cases_trend", "adm", "adm_trend"))) %>%
  dplyr::filter(!is.na(id)) %>%
  ggplot(aes(x = date, y = value, col = name)) +
  geom_line() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  facet_wrap(. ~ id) +
  scale_color_brewer(palette = "Paired") +
  labs(x = "Date", y = "Value (standardised)",
       col = "Data") +
  theme_bw() +
  theme(legend.position = "top")

```

## Cross-correlation, text
```{r cc text}

# National
corr_nat %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr, na.rm = TRUE)) %>%
  dplyr::filter(corr > 0.99*max(corr))

# By NHS region
corr_reg %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr, na.rm = TRUE)) %>%
  dplyr::filter(corr > 0.99*max(corr))

```

## Cross-correlation, tile

```{r cc tile}

g_tile_nat <- corr_nat %>%
  dplyr::filter(lag_days <= 10) %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from)) %>%
  ggplot(aes(x = forecast_from, y = lag_days, fill = corr)) +
  geom_tile() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  scale_y_continuous(breaks = integer_breaks()) +
  scale_fill_distiller(palette = "RdBu", limits = c(-1, 1)) +
  facet_wrap(. ~ id) +
  labs(x = "Forecast date", y = "Lag (days)",
       title = "A",
       fill = "Correlation") +
  theme_bw() +
  theme(legend.position = "none")

g_tile_reg <- corr_reg %>%
  dplyr::filter(lag_days <= 10,
                !is.na(id)) %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from)) %>%
  ggplot(aes(x = forecast_from, y = lag_days, fill = corr)) +
  geom_tile() +
  scale_x_date(date_breaks = "4 weeks",
               date_labels = "%d %b",
               limits = c(as.Date("2020-08-01"), NA)) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  scale_fill_distiller(palette = "RdBu", limits = c(-1, 1)) +
  facet_wrap(. ~ id, ncol = 2) +
  labs(x = "Forecast date", y = "Lag (days)",
       title = "B",
       fill = "Correlation") +
  theme_bw() +
  theme(legend.position = "top")

#####
guide_area() / (g_tile_nat | g_tile_reg) +
  plot_layout(heights = c(0.1, 1), guides = "collect")
#####

```

## Cross-correlation, line

```{r cc line}

g_correlation_nat <- corr_nat %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr)) %>%
  ggplot(aes(x = lag_days, y = corr)) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  scale_y_continuous(limits = c(0.5, 1)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Lag (days)", y = "Correlation",
       col = "NHS region",
       title = "A") +
  theme_bw()

g_correlation_reg <- corr_reg %>%
  dplyr::filter(!is.na(id)) %>%
  dplyr::group_by(id, lag_days) %>%
  dplyr::summarise(corr = mean(corr)) %>%
  ggplot(aes(x = lag_days, y = corr)) +
  geom_line(aes(col = id), lwd = 0.6) +
  geom_line(data = corr_reg %>%
              dplyr::filter(!is.na(id)) %>%
              dplyr::group_by(lag_days) %>%
              dplyr::summarise(corr = mean(corr)), lwd = 0.6, lty = 2) +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  scale_y_continuous(limits = c(0.5, 1)) +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2") +
  labs(x = "Lag (days)", y = "",
       col = "NHS region",
       title = "B") +
  theme_bw()

#####
g_correlation_nat | g_correlation_reg
#####

```


# Extra

```{r penalised regression, eval = FALSE, include = FALSE}

pen_nat <- purrr::map_df(.x = forecast_dates, .f = ~ {
  
  df_pen_in <- df_nat %>%
  dplyr::select(id, date, adm_trend, contains("cases"), -cases) %>%
  dplyr::rename(adm = adm_trend,
                cases = cases_trend) %>%
  dplyr::filter(date > as.Date(.x) - 42,
                date <= as.Date(.x)) %>%
  dplyr::mutate(across(contains("cases"), ~.x/sd(.x))) %>%
  dplyr::mutate(adm = adm/sd(adm))

  y_in <- df_pen_in$adm
  x_in <- df_pen_in %>%
    dplyr::select(contains("case")) %>%
    dplyr::mutate(ones = rep(1, length(y_in))) %>%
    as.matrix()
  
  cv_ridge <- cv.glmnet(x_in, y_in, alpha = 0)
  cv_ridge$lambda.min
  model_ridge <- glmnet(x_in, y_in, alpha = 0, lambda = cv_ridge$lambda.min)
  out_ridge <- as.matrix(coef(model_ridge))
  tb_ridge <- tibble::tibble(name = rownames(out_ridge), value = out_ridge[,1]) %>%
    dplyr::filter(grepl("case", name)) %>%
    dplyr::mutate(forecast_from = .x,
                  method = "ridge")
  
  cv_lasso <- cv.glmnet(x_in, y_in, alpha = 1)
  cv_lasso$lambda.min
  model_lasso <- glmnet(x_in, y_in, alpha = 1, lambda = cv_lasso$lambda.min)
  out_lasso <- as.matrix(coef(model_lasso))
  tb_lasso <- tibble::tibble(name = rownames(out_lasso), value = out_lasso[,1]) %>%
    dplyr::filter(grepl("case", name)) %>%
    dplyr::mutate(forecast_from = .x,
                  method = "lasso") 
  
  tb_out <- tb_ridge %>%
    dplyr::bind_rows(tb_lasso)
  
  return(tb_out)
  
} ) %>%
  dplyr::bind_rows()

pen_grid = tidyr::expand_grid(date = forecast_dates, region = unique(df_reg$id))

pen_reg <- purrr::map2_df(.x = pen_grid$date, .y = pen_grid$region, .f = ~ {
  
  df_pen_in <- df_reg %>%
  dplyr::select(id, date, adm_trend, contains("case"), -case) %>%
  dplyr::rename(adm = adm_trend,
                case = case_trend) %>%
  dplyr::filter(id == .y,
                date > as.Date(.x) - 42,
                date <= as.Date(.x)) %>%
  dplyr::mutate(across(contains("case"), ~.x/sd(.x))) %>%
  dplyr::mutate(adm = adm/sd(adm)) %>%
    dplyr::ungroup()

  y_in <- df_pen_in$adm
  x_in <- df_pen_in %>%
    dplyr::select(adm, contains("case"))
  x_in <- model.matrix(adm ~ ., x_in)[,-1]
  
  cv_ridge <- cv.glmnet(x_in, y_in, alpha = 0)
  cv_ridge$lambda.min
  model_ridge <- glmnet(x_in, y_in, alpha = 0, lambda = cv_ridge$lambda.min)
  out_ridge <- as.matrix(coef(model_ridge))
  tb_ridge <- tibble::tibble(name = rownames(out_ridge), value = out_ridge[,1]) %>%
    dplyr::filter(grepl("case", name)) %>%
    dplyr::mutate(forecast_from = .x,
                  method = "ridge")
  
  cv_lasso <- cv.glmnet(x_in, y_in, alpha = 1)
  cv_lasso$lambda.min
  model_lasso <- glmnet(x_in, y_in, alpha = 1, lambda = cv_lasso$lambda.min)
  out_lasso <- as.matrix(coef(model_lasso))
  tb_lasso <- tibble::tibble(name = rownames(out_lasso), value = out_lasso[,1]) %>%
    dplyr::filter(grepl("case", name)) %>%
    dplyr::mutate(forecast_from = .x,
                  method = "lasso") 
  
  tb_out <- tb_ridge %>%
    dplyr::bind_rows(tb_lasso) %>%
    dplyr::mutate(region = .y)
  
  return(tb_out)
  
} ) %>%
  dplyr::bind_rows()

```

```{r ARIMA regression fit}

map_grid <- expand.grid(x_var = c("cases", paste0("cases_", 1:7)), fdate = forecast_dates)

fit_nat <- purrr::map2_df(.x = map_grid$x_var, .y = map_grid$fdate, .f = ~{
  
  df_in <- df_nat %>%
  dplyr::select(id, date, adm_trend, contains("cases"), -cases) %>%
  dplyr::rename(adm = adm_trend,
                cases = cases_trend) %>%
  dplyr::filter(date > as.Date(.y) - 42,
                date <= as.Date(.y))
  
  fit <- forecast::auto.arima(y = df_in$adm,
                            xreg = df_in %>% pull(.x))
  
  out <- tibble::tibble(forecast_date = .y, var = .x, aic = fit$aic, bic = fit$bic, aicc = fit$aicc)
  
  return(out)
  
}) %>%
  dplyr::bind_rows()


map_grid <- expand.grid(x_var = c("case", paste0("case_", 1:7)), fdate = forecast_dates)

fit_reg <- purrr::map2_df(.x = map_grid$x_var, .y = map_grid$fdate, .f = ~{
  
  out <- purrr::map_df(.x = unique(df_pen_reg$id), .f = ~ {
    
    
    
  })
  
  df_in <- df_pen_reg %>%
    dplyr::filter(id == "Midlands") %>%
    dplyr::filter(date > as.Date(.y) - 42,
                  date <= as.Date(.y))
  
  fit <- forecast::auto.arima(y = df_in$adm,
                            xreg = df_in %>% pull(.x))
  
  out <- tibble::tibble(forecast_date = .y, var = .x, aic = fit$aic, bic = fit$bic, aicc = fit$aicc)
  
  return(out)
  
}) %>%
  dplyr::bind_rows()


```

## Penalised regression

```{r lasso national, eval = FALSE}

pen_nat %>%
  dplyr::select(method, forecast_from, name, value) %>%
  dplyr::filter(method == "lasso") %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from),
                name = ifelse(name == "cases", 0, as.integer(str_remove(name, "cases_"))),
                value = ifelse(value == 0, NA, value)) %>%
  ggplot(aes(x = forecast_from, y = name, fill = value)) +
  geom_tile() +
  scale_x_date(date_breaks = "4 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = seq(0, 7, 1)) +
  scale_fill_distiller(palette = "RdBu", na.value = "grey80", limits = c(-2, 2)) +
  labs(x = "Forecast date", y = "Lag (days)",
       title = "LASSO regression") +
  theme_bw()

pen_nat %>%
  dplyr::select(method, forecast_from, name, value) %>%
  dplyr::filter(method == "ridge") %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from),
                name = ifelse(name == "cases", 0, as.integer(str_remove(name, "cases_"))),
                value = ifelse(value == 0, NA, value)) %>%
  ggplot(aes(x = forecast_from, y = name, fill = value)) +
  geom_tile() +
  scale_x_date(date_breaks = "4 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = seq(0, 7, 1)) +
  scale_fill_distiller(palette = "RdBu", na.value = "grey50", limits = c(-0.6, 0.6)) +
  labs(x = "Forecast date", y = "Lag (days)",
       title = "Ridge regression",
       fill = "Coefficient") +
  theme_bw()

pen_reg %>%
  dplyr::select(method, region, forecast_from, name, value) %>%
  dplyr::filter(method == "lasso") %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from),
                name = ifelse(name == "case", 0, as.integer(str_remove(name, "case_"))),
                value = ifelse(value == 0, NA, value)) %>%
  ggplot(aes(x = forecast_from, y = name, fill = value)) +
  geom_tile() +
  facet_wrap(. ~ region) +
  scale_x_date(date_breaks = "4 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = seq(0, 7, 1)) +
  scale_fill_distiller(palette = "RdBu", na.value = "grey80", limits = c(-5, 5)) +
  labs(x = "Forecast date", y = "Lag (days)") +
  theme_bw()

pen_reg %>%
  dplyr::select(method, region, forecast_from, name, value) %>%
  dplyr::filter(method == "ridge") %>%
  dplyr::mutate(forecast_from = as.Date(forecast_from),
                name = ifelse(name == "case", 0, as.integer(str_remove(name, "case_"))),
                value = ifelse(value == 0, NA, value)) %>%
  ggplot(aes(x = forecast_from, y = name, fill = value)) +
  geom_tile() +
  facet_wrap(. ~ region) +
  scale_x_date(date_breaks = "4 weeks", date_labels = "%d %b") +
  scale_y_continuous(breaks = seq(0, 7, 1)) +
  scale_fill_distiller(palette = "RdBu", na.value = "grey50", limits = c(-0.8, 0.8)) +
  labs(x = "Forecast date", y = "Lag (days)") +
  theme_bw()


```


## Fit ARIMA regression

```{r arima and cases, eval = FALSE}



fit_nat %>%
  dplyr::mutate(var = ifelse(var == "cases", 0, as.integer(str_remove(var, "cases_"))),
                forecast_date = as.Date(forecast_date)) %>%
  ggplot(aes(x = var, y = aic)) +
  geom_point() +
  facet_wrap(. ~ forecast_date) +
  scale_x_continuous(breaks = 0:7) +
  labs(x = "Lag (days)", y = "AIC") +
  theme_bw()

fit_nat %>%
  dplyr::mutate(var = ifelse(var == "cases", 0, as.integer(str_remove(var, "cases_"))),
                forecast_date = as.Date(forecast_date)) %>%
  dplyr::group_by(forecast_date) %>%
  dplyr::filter(aic == min(aic)) %>%
  ggplot(aes(x = forecast_date, y = var)) +
  geom_line()



fit_reg %>%
  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
  dplyr::group_by(forecast_date) %>%
  dplyr::filter(aic == min(aic))

fit_reg %>%
  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
  ggplot(aes(x = var, y = aic)) +
  geom_point() +
  facet_wrap(. ~ forecast_date) +
  # scale_x_date(date_breaks = "4 weeks", date_labels = "%d %b") +
  theme_bw()



```

